---
title: "GCI_jumps"
author: "Radosław Rybakowski"
date: "2023-12-17"
output: html_document
---
#Wykrywanie jumpów na GCI i GWI
###Biblioteki

```{r, echo = FALSE}
library(tidyverse)
library(writexl)
library(panelView)
library(PanelMatch)

data <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\2_Przetwarzanie_danych\Data_merging\database_2023_12_16.xlsx)")

dict_GCI <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\dict_master.xlsx)",
										sheet = "GCI") %>% 
	mutate(variables = paste0("wf_", variables))

dict_cou <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\dict_master.xlsx)")
```
## Writing function to detect jump:
Assume, that jump exist if:
  * in period equal "jump_years" we have jump larger or equal "min_jump",
  * in period "check_years" - number of years after potential jump, 
  level of variable doesn't drop, so jump is sustained

```{r Function to detect jumps, include=FALSE}
ii = 1
detect_jump <- function(
				vector,
				jump_years = 3,
				check_years = 3,
				min_jump = 0.5){
	len_vector = length(vector)
	vector_output <- rep(0,len_vector)
	for (ii in 1:len_vector){
		# Count years which are necessary for letter actions
		if(len_vector - (ii+jump_years-1) <  check_years){
			# print(ii)
			break
		}
		
		jump_period <- vector[ii:(ii+jump_years-1)]
		# if(any(is.na(jump_period))){
		# 	# print(ii)
		# 	next
		# }
		# Calculate a jump a check threshold (min_jump)
		jump <- jump_period[jump_years]-jump_period[1]
		if(jump < min_jump){
			# print(ii)
			next
		}
		# Check if in year in control period value level was lower that in the moment of jump
		if(any(vector[(ii+jump_years):len_vector] - jump_period[jump_years] < 0)){
			# print(ii)
			next
		}
		earlier <- 0
		
		for(jj in 1:(length(jump_period)-2)){
			jump <- jump_period[jump_years-jj]-jump_period[1]
			if(jump < min_jump){
				# print(ii)
				next
			}
			if(any(vector[(ii+jump_years-jj):len_vector] - jump_period[jump_years-jj] < 0)){
				# print(ii)
				next
			}
			earlier <- jj
		}
		
		# print((ii+jump_years):len_vector)
		vector_output[(ii+jump_years - earlier):len_vector] <- 1
		if(sum(vector_output) >0){
			break
		}
	}	
	return(vector_output)
}

vector <- c(1,1,3,3,3,3,3,3,3)
vector
# 
detect_jump(vector,
				jump_years = 4,
				check_years = 2,
				min_jump = 0.5)


```

```{r Calculating jumps}

data_wf <- data %>% 
	select(cou, year, starts_with("wf")) 

data_group <- data_wf %>% 
	select(-wf_TBPC) %>% #zmienna przyjmuje wartość zero
	group_by(cou) %>% 
	arrange(cou, year) 

data_dynamics <- data_group %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~.x/dplyr::lag(.x)
	)) %>% 
	filter(year != 2008) %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~ purrr::accumulate(.x, \(acc, nxt) acc*nxt)
	)) 
	
data_jumps <- data_dynamics %>%
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~detect_jump(.x,
				jump_years = 2,
				check_years = 3,
				min_jump = 0.1)
	))

```
### Jumps sumamry - które zmienne pokazują dużo ilość krajów z treatmentem?
```{r jumps_summary}
data_jumps %>% 
	summarize(across(
		.cols = starts_with("wf"),
		.fns = max
	)) %>% 
	ungroup() %>% 
	summarize(across(
		.cols = starts_with("wf"),
		.fns = sum
	)) %>% 
	pivot_longer(
		starts_with("wf")
	) %>% 
	arrange(desc(value)) %>% 
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series)

```

## Graph - visualization

```{r countries_treated}


treated_columns <- function(column){
	column <- enquo(column)	
	filter_jumps <- data_jumps %>% 
		select(year, cou, !!column) %>%
		pivot_wider(names_from = cou,
						values_from = !!column) %>% 
		select(where(~sum(.x) > 0)) %>% 
		colnames()
}

filter_jumps <- treated_columns(wf_EOSQ041)
dict_cou %>% 
	filter(cou %in% filter_jumps)

```

```{r countries jumps line plot}
visual_jumps <- function(column){
	column <- enquo(column)	
	filter_jumps <- treated_columns(!!column)
	data_group %>% 
		select(year, cou, !!column) %>% #select_data
		filter(cou %in% filter_jumps) %>% 
		mutate(year = as.Date(paste0(year,"-01-01"))) %>% 
		ggplot(aes(year, !!column)) +
		geom_line(aes(color = cou)) +
		theme_minimal()
}

visual_jumps(wf_EOSQ041)

```
```{r Panel visualization}
visual_panel <- function(column){
column <- enquo(column)	
column_str <- quo_name(column)
panelview(as.formula(paste0("1 ~ ", column_str)),
          data = data_jumps %>% 
				select(year, cou, !!column) %>% 
			 	filter(cou %in% filter_jumps),
			 index = c("cou","year"),
			 legendOff = TRUE,
			 gridOff = TRUE,
			 by.timing = TRUE)
} 

# plotly::ggplotly(visual_panel(wf_GCI))
visual_panel(wf_EOSQ041)
```
## Modelling part


```{r prepare data to model}

data_to_model <- function(column){
	column <- enquo(column)	
	output <- data %>%
		select(year, cou, y, starts_with("pn")) %>% 
		left_join(data_jumps %>% 
					 	select(year, cou, !!column),
					  by = join_by(year, cou)) %>% 
		rename(treatment = !!column) %>% 
		mutate(treatment = ifelse(year == 2008, 0, treatment)) %>% 
		mutate(cou = as.integer(as.factor(cou))) %>% 
		mutate(year = as.integer(year)) %>% 
		select(-pn_pop, -pn_rgdpna) %>% 
		arrange(cou, year) %>% 
		as.data.frame()
	return(output)
}

data_model <- data_to_model("wf_EOSQ041")

# unique(data_model$year)
# DisplayTreatment(unit.id = "cou",
#                  time.id = "year", 
#                  legend.position = "none",
#                  xlab = "year", 
#                  ylab = "Individual id",
#                  treatment = "treatment",
# 					  # matched.set = PM.results,
# 					  # show.set.only = TRUE,
# 					  data = data_model)

```

```{r Panel Match - define matching and set formula, message=FALSE, warning=FALSE, include=FALSE}
my_matching <- function(x){
	output <- list()
	for (ii in c("mahalanobis", "ps.match", "CBPS.match", "ps.weight", "CBPS.weight")){
		PM.results <- PanelMatch(
			lag = 2, 
			time.id = "year", 
			unit.id = "cou", 
			treatment = "treatment", 
			refinement.method = ii,
			data = data_model, 
			match.missing = TRUE, 
			covs.formula = ~ 
			 # I(lag(pn_csh_x, 1:3)) + #Share of merchandise exports at current PPPs
			 I(lag(pn_csh_i, 1:2)) + #Share of gross capital formation at current PPPs
			 I(lag(y, 1:2)) + 
			 I(lag(pn_csh_g, 1:2)) + #Share of government consumption at current PPPs
			 I(lag(pn_hc, 1:2)) #Human capital index, based on years of schooling and returns to education
			, 
			size.match = 10,
			qoi = "att" ,
			outcome.var = "y",
			lead = 0:2, 
			forbid.treatment.reversal = FALSE,
			use.diagonal.variance.matrix = TRUE
			)
		PE.results <- PanelEstimate(sets = PM.results, data = data_model)
		output[[ii]] <- summary(PE.results)$summary
	}
	return(output)
}
results <- my_matching()

```
```{r, results}
results
```



