# GDP growth caused by GCI indicators jumps with PanelMatch package

### Libraries

```{r Funkcje, echo=FALSE}
source("matching_functions.R")

```

```{r Biblioteki, echo = FALSE, include = FALSE}
library(tidyverse)
library(writexl)
library(panelView)
library(PanelMatch)
library(furrr)
library(readxl)
library(kableExtra)

# data <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\2_Przetwarzanie_danych\Data_merging\database_2023_12_22.xlsx)")

data <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\2_Przetwarzanie_danych\Data_merging\database_2023_12_29.xlsx)")

dict_GCI <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\dict_master.xlsx)",
										sheet = "GCI") %>% 
	mutate(variables = paste0("wf_", variables))

dict_cou <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\dict_master.xlsx)")
```

## Function to detect a jump

Assume, that jump exist if:

-   In period equal "jump_years" we have jump larger or equal "min_jump",

-   In period "check_years" - number of years after potential jump, level of variable doesn't drop, so jump is sustained

```{r Function to detect jumps}

vector <- c(1,1,3,3,3,3,3,1,3)

temp <- detect_jump(vector,
				jump_years = 1,
				check_years = 1,
				min_jump = 0.025)

temp
```

```{r Calculating jumps}

data_wf <- data %>% 
	select(cou, year, starts_with("wf")) 

data_group <- data_wf %>%
	select(-wf_TBPC) %>% #zmienna przyjmuje wartość zero
	group_by(cou) %>%
	arrange(cou, year)

data_dynamics <- data_group %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~.x/dplyr::lag(.x)
	)) %>% 
	filter(year != 2008) %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~ purrr::accumulate(.x, \(acc, nxt) acc*nxt)
	)) 
```

```{r, choosing jumps}
jumps_args <- list(
				is.dynamic = FALSE,
				jump_years = 2,
				check_years = 2,
				min_jump = 0.25)

data_jumps <- jump_data_proces(jumps_args)

```

### Jumps summary - which variables have large number of countries?

```{r jumps_summary}
jumps_sum_df <- jumps_summary()

jumps_sum_df
```

## Jumps visualization

```{r countries_treated}
filter_jumps <- treated_columns(wf_GCI.A)
dict_cou %>% 
	filter(cou %in% filter_jumps) %>% 
	select(cou, country)

```

```{r countries jumps line plot}
visual_jumps(wf_GCI.A)
```

```{r Panel visualization}
visual_panel(wf_GCI.A)
```

## Modelling

Choose appropiate variable to model

```{r prepare data to model}
data_model <- data_to_model(wf_EOSQ118)


```

Perform matching

```{r Panel Match, include = FALSE}

results <- suppressWarnings(invisible(
	my_matching(outcome = "y_ham",
				   iterations = 1000,
					matching_methods = c("CBPS.match","CBPS.weight"))
	))

```

```{r covariate balance}
my_matching(outcome = "y_ham",
				   iterations = 1000,
					matching_methods = c("CBPS.match","CBPS.weight"),
				get_balance = TRUE)

```

### Test all variables within one jump definition

```{r vars_to_col}
vars_to_test <- jumps_sum_df %>% 
	# filter(value > 10) %>%
	select(name) %>%  
	unlist()
# vars_to_test
names(vars_to_test) <- vars_to_test
vars_to_test_col <- vars_to_test
```

```{r test many vars, include=FALSE}

test_variables <- function(var){
	data_model <- data_to_model({{var}}) # to trzeba poprawić
	results <- my_matching(iterations = 100,
								  df = data_model)
	results_df <- tibble(results = results) %>%
		mutate(results = map(results, .f = ~as.data.frame(.x))) %>% 
		mutate(names = names(results)) %>%
		unnest(cols = c(results)) %>% 
		select(names, everything())
	results_df
}
plan(multisession, workers = 4)
results_list <- furrr::future_map(vars_to_test,test_variables,
											 .options = furrr_options(seed = 123))
print("finish")
```

```{r Test summary}

all_df <- tibble(results = results_list) %>%
	mutate(variable = names(results)) %>%
	unnest(cols = c(results)) 
all_df_summary <- all_df %>%
	mutate(check = ifelse(`5%`> -0.005, 1, 0)) %>% 
	group_by(variable) %>% 
	summarize(sig_positive = mean(check)) %>% 
	left_join(dict_GCI, by = c("variable" = "variables")) %>% 
	arrange(desc(sig_positive))

# list_to_save <- list(all_df, all_df_summary)
# writexl::write_xlsx(list_to_save, "jumps_33_004_d_yham.xlsx")
all_df_summary


```

### Test one variable among many jumps definitions.

```{r,include=FALSE}
jumps_args_list <- list(
	is.dynamic = c(TRUE, FALSE),
	jump_years = 1:3,
	check_years = 2:5,
	min_jump = 
		seq(from = 0.01,
			by = 0.01,
				length.out = 10)) %>% 
	cross()

column <- "wf_GCI.A.04"

data_onevar <- one_var_df_proc(column = !!column)

vars_to_test <- data_onevar %>% 
	select(-year) %>% 
	group_by(cou) %>% 
	summarize(across(.cols = everything(),
						  .fns = max)) %>% 
	ungroup() %>% 
	select(-cou) %>% 
	select(where(~sum(.x)>15) & where(~sum(.x)<45) ) %>% ## only jumps where minimum 10 countries were detected
	colnames()


names(vars_to_test) <- vars_to_test


plan(multisession, workers = 4)
results_list <- furrr::future_map(vars_to_test, test_one_variable,
											 .options = furrr_options(seed = 123))
print("finish")

```

```{r}
all_df <- tibble(results = results_list) %>%
	mutate(variable = names(results)) %>%
	unnest(cols = c(results)) 
all_df_summary <- all_df %>%
	mutate(check_1  = ifelse(`5%`> 0.00, 1, 0)) %>%
	mutate(check_2  = ifelse(`95%`< 0.00, 1, 0)) %>%
	group_by(variable) %>%
	summarize(sig_positive = mean(check_1),
				 sig_negative = mean(check_2)) %>%
	arrange(desc(sig_negative))


list_to_save <- list(all_df, all_df_summary)
# writexl::write_xlsx(list_to_save, paste0("results/jumps_",column,"_yham.xlsx"))

all_df_summary 

```

```{r}
# data_model %>% 
# 	left_join(data_onevar %>% 
# 				 		mutate(cou = as.integer(as.factor(cou)))) %>%
# 	filter(year != 2008) %>% 
# 	select(cou, year, `1_3_2_0.1`, treatment) %>% 
# 	ungroup() %>% 
# 	summarize(x = sum(abs(`1_3_2_0.1`- treatment)))

```

### Test all combinations: many variables & many jump definition

```{r, include = FALSE}
test_everything <- function(variable){
	# variable <- enquo(variable)
	jumps_args_list_1 <- list(
	is.dynamic = c(FALSE),
	jump_years = 1:3,
	check_years = 2:3,
	min_jump = 
		seq(from = 0.1,
			by = 0.05,
				length.out = 20)) %>% cross()
	jumps_args_list_2 <- list(
		is.dynamic = c(TRUE),
		jump_years = 1:3,
		check_years = 2:3,
		min_jump = 
			seq(from = 0.05,
				by = 0.01,
					length.out = 20)) %>% cross()
	jumps_args_list <- append(jumps_args_list_2, jumps_args_list_1)

	data_onevar <- one_var_df_proc(column = !!variable) %>% 
		filter(year != 2008)
	vars_to_test <- data_onevar %>% 
		select(-year) %>% 
		group_by(cou) %>% 
		summarize(across(.cols = everything(),
							  .fns = max)) %>% 
		ungroup() %>% 
		select(-cou) %>%  
		select(where(~sum(.x) > 20) & where(~sum(.x) < 50) ) %>% 
		colnames()
	
	counts <- data_onevar %>%
		select(cou, all_of(vars_to_test)) %>% 
		group_by(cou) %>% 
		summarize(across(.cols = everything(),
							  .fns = max)) %>% 
		ungroup() %>% 
		select(-cou) %>% 
		summarize(across(.cols = everything(),
							  .fns = sum)) %>% 
		pivot_longer(cols = everything()) %>% 
		rename(count = value) %>% 
		rename(variable = name)
	# return(counts)
	
	if (length(vars_to_test) == 0){
		return(NULL)
	}
	names(vars_to_test) <- vars_to_test
	# return(list(vars_to_test, data_onevar))
	results_list <- map(vars_to_test, 
			  .f = ~test_one_variable(.x, 
  						data_one = data_onevar))
	all_df <- tibble(results = results_list) %>%
			mutate(variable = names(results)) %>%
			unnest(cols = c(results)) %>% 
			left_join(counts, by = "variable")
	all_df_summary <- all_df %>%
		mutate(check_1  = ifelse(`5%`> 0.00, 1, 0)) %>%
		mutate(check_2  = ifelse(`95%`< 0.00, 1, 0)) %>%
		group_by(variable, count) %>%
		summarize(sig_positive = mean(check_1),
					 sig_negative = mean(check_2)) %>%
		arrange(desc(sig_positive)) 
		
	list_to_save <- list(all_df, all_df_summary)
	writexl::write_xlsx(list_to_save, paste0("results_2023_12_29/jumps_",variable,"_yham.xlsx"))
	return(list(df = all_df_summary, name = variable))
}
 

plan(multisession, workers = 8)
final_results <- future_map(rest_to_test, safely(test_everything), .progress = TRUE,
			  .options = furrr_options(seed = 123))
print("finish")


```

```{r,echo=FALSE}
final_results_df <- final_results

final_results_sig_positive <- final_results_df %>% 
	map(.f = ~.x$result$df) %>% 
	map2(.y = names(final_results_df), ~.x %>% 
		  	cbind(name = .y)) %>% 
	discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-sig_negative) %>% 
		 	pivot_wider(values_from = sig_positive)) %>% 
	reduce(.f = full_join, by = join_by(variable))

final_results_sig_negative <- final_results_df %>% 
	map(.f = ~.x$result$df) %>% 
	map2(.y = names(final_results_df), ~.x %>% 
		  	cbind(name = .y)) %>% 
	discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-sig_positive) %>% 
		 	pivot_wider(values_from = sig_negative)) %>% 
	reduce(.f = full_join, by = join_by(variable))
# write_xlsx(final_results_tibble, "results_all.xlsx")
```

```{r}
final_results_sig_negative  %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	group_by(name) %>% 
	summarize(value = max(value)) %>% 
	arrange(desc(value)) %>% 
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series)
```

### Reading files with results from folder

```{r}

results_files <- list.files("results_2023_12_29") 

filter_temp <- results_files %>% str_remove("jumps_") %>% str_remove("_yham.xlsx")
rest_to_test <- vars_to_test_col[!vars_to_test_col %in% filter_temp]

final_results_read <- paste0("results_2023_12_29\\", results_files) %>% 
	map(.f = function(x){
		sheet1 <- read_xlsx(x, sheet = "Sheet1")
		sheet2 <- read_xlsx(x, sheet = "Sheet2")
		to_return <- list(
			Sheet1 = sheet1,
			Sheet2 = sheet2,
			name = x %>% 
				str_remove("results_2023_12_29\\\\") %>% 
				str_remove("jumps_") %>%
				str_remove("_yham.xlsx"))
	}) 
```
### How significance of results is distributed?
```{r}

final_results_sig_positive <- 
	final_results_read %>% 
	map(.f = ~.x$Sheet2) %>% 
	map2(.y = final_results_read, 
		  ~.x %>% cbind(name = .y$name)) %>% 
	# discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-c(count, sig_negative)) %>% 
		 	pivot_wider(values_from = sig_positive)) %>% 
	reduce(.f = full_join, by = join_by(variable)) %>% 
	arrange(variable)

final_results_sig_negative <- 
	final_results_read %>% 
	map(.f = ~.x$Sheet2) %>% 
	map2(.y = final_results_read, 
		  ~.x %>% cbind(name = .y$name)) %>% 
	# discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-c(count, sig_positive)) %>% 
		 	pivot_wider(values_from = sig_negative)) %>% 
	reduce(.f = full_join, by = join_by(variable)) %>% 
	arrange(variable)
# writexl::write_xlsx(list(
# 	final_results_sig_negative,
# 	final_results_sig_positive),
# 	"all_results_2023_12_29.xlsx"
# )
```

```{r}
sig_pos_summary <- final_results_sig_positive  %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	group_by(name) %>% 
	summarize(value = max(value, na.rm = TRUE)) %>%
	# summarize(value = mean(value, na.rm = TRUE)) %>%
	arrange(desc(value)) %>% 
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series) %>% 
	rename(pos = value)

sig_neg_summary <- final_results_sig_negative  %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	group_by(name) %>% 
	summarize(value = max(value, na.rm = TRUE)) %>%
	# summarize(value = mean(value, na.rm = TRUE)) %>%
	arrange(desc(value)) %>%
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series) %>% 
	rename(neg = value)

all_summary <- sig_neg_summary %>% 
	left_join(sig_pos_summary,
				 by = join_by(name, series)) %>% 
	select(name, neg, pos, series) %>% 
	filter(!str_detect(name, "\\.\\w{1}\\.\\d{2}")) %>% 
	arrange(desc(pos))

all_summary

```

```{r}
final_results_sig_positive %>% 
	summarize(across(
		-variable,
		.fns = ~mean(.x, na.rm = TRUE)
	)) %>% 
	pivot_longer(everything()) %>% 
	summarize(value = mean(value))

final_results_sig_negative %>% 
	summarize(across(
		-variable,
		.fns = ~mean(.x, na.rm = TRUE)
	)) %>% 
	pivot_longer(everything()) %>% 
	summarize(value = mean(value))
```
### Sprawdźmy jakie są oszacowania tych parametrów

```{r}
final_estimates <- final_results_read %>% 
	map(.f = ~.x$Sheet1 %>% 
		 	mutate(name = .x$name)) %>% 
	reduce(bind_rows) %>% 
	group_by(variable, name) %>% 
	mutate(sig_pos = ifelse(`5%` > 0,1,0), 
			 sig_neg = ifelse(`95%` < 0, 1,0)) %>% 
	summarize(across(
		.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	group_by(name) %>% 
	summarize(across(
		.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	ungroup()

final_est_by_year  <- 
	final_results_read %>%
	map(.f = ~.x$Sheet1 %>% 
		 	mutate(name = .x$name)) %>% 
	reduce(bind_rows)  %>%
	# filter(str_detect(name, "\\.\\w{1}\\.\\d{2}")) %>% 
	filter(names == "CBPS.match") %>% 
	separate(variable,
				into = c("is.dynamic",
						  "jump_years",
						  "check_years",
						  "min_jump"),
				sep = "_") %>% 
	filter(is.dynamic == 0 & min_jump > 0.25 |
			 is.dynamic == 1 & min_jump > 0.05) %>% 
	unite(all_of(c("is.dynamic",
			  "jump_years",
			  "check_years",
			  "min_jump")),
			col = "variable") %>% 
	mutate(sig_pos = ifelse(`5%` > 0,1,0), 
			 sig_neg = ifelse(`95%` < 0, 1,0)) %>% 
	group_by(variable, name, names) %>% 
	mutate(year = row_number()) %>% 
	group_by(variable, name, year) %>%  
	summarize(across(
		.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	group_by(name, year) %>% 
	summarize(across(
		.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	ungroup()  %>% 
	pivot_wider(values_from = all_of(c('estimate', 'sig_pos', 'sig_neg')), 
					names_from = year,
					names_glue = "{.value}_{year}") 

final_est_by_year_sum <- 
	final_est_by_year %>% 
	mutate(across(
		.cols = contains("estimate"),
		.fns = ~ifelse(.x > 0, 1, 0)))
summary(final_est_by_year_sum)
summary(final_est_by_year)



final_est_by_year %>% 
	ggplot(aes(x = estimate_3)) + 
	geom_histogram(bins = 15)
```

## Nie zbyt mądra próba modelowania, czy parametr ma wpływ na zmienną?

```{r}

final_results_sig_negative %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	rename(sig_neg = value) %>% 
	left_join(final_results_sig_positive %>% 
	 	pivot_longer(-variable) %>% 
		drop_na() %>% 
		rename(sig_pos = value)) %>% 
	mutate(value = sig_pos - sig_neg) %>% 


```

```{r}
df_test_model <- 
	final_results_read %>% 
	map(.f = ~.x$Sheet2) %>% 
	map2(.y = final_results_read, 
		  ~.x %>% cbind(name = .y$name)) %>% 
	reduce(.f = full_join,
			 by = join_by(variable, count, sig_positive, sig_negative, name)) %>% 
	left_join(final_results_read %>% 
		map(.f = ~.x$Sheet1 %>% 
			 	mutate(name = .x$name)) %>% 
		reduce(bind_rows) %>% 
		group_by(variable, name) %>% 
		mutate(sig_pos = ifelse(`5%` > 0,1,0), 
				 sig_neg = ifelse(`95%` < 0, 1,0)) %>% 
		summarize(across(
			.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
			.fns = mean
		))) %>% 
	arrange(variable) %>% 
	separate(variable,
				into = c("is.dynamic",
						  "jump_years",
						  "check_years",
						  "min_jump"),
				sep = "_") %>% 
	mutate(sig_sum = sig_positive - sig_negative) %>% 
	mutate(across(-name,
					  .fns = ~as.numeric(.x))) %>% 
	mutate(sig_bin = ifelse(sig_sum > 0, 1, 0))


```

```{r}
model_lm <- lm(estimate ~ is.dynamic +
						factor(is.dynamic):factor(jump_years) + 
						factor(min_jump) +
						factor(is.dynamic):factor(check_years) +
						factor(is.dynamic):count +
						name,
						data = df_test_model
						)
summary(model_lm)

# model_glm <- glm(sig_bin ~ is.dynamic +
# 						factor(is.dynamic):jump_years + 
# 						factor(is.dynamic):min_jump +
# 						factor(is.dynamic):check_years +
# 						factor(is.dynamic):count +
# 						name,
# 						data = df_test_model,
# 						family = binomial(link = "logit")
# 						)
# summary(model_glm)

# citation("PanelMatch")
# glue::glue_collapse(vars_to_test_col, sep = "\n")
```
