# GDP growth caused by GCI indicators jumps with PanelMatch package

### Libraries

```{r Funkcje, echo=FALSE}
source("matching_functions.R")

```

```{r Biblioteki, echo = FALSE, include = FALSE}
library(tidyverse)
library(writexl)
library(panelView)
library(PanelMatch)
library(furrr)
library(kableExtra)

data <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\2_Przetwarzanie_danych\Data_merging\database_2023_12_22.xlsx)")

dict_GCI <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\dict_master.xlsx)",
										sheet = "GCI") %>% 
	mutate(variables = paste0("wf_", variables))

dict_cou <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\dict_master.xlsx)")
```

## Function to detect a jump

Assume, that jump exist if:

-   In period equal "jump_years" we have jump larger or equal "min_jump",

-   In period "check_years" - number of years after potential jump, level of variable doesn't drop, so jump is sustained

```{r Function to detect jumps}

vector <- c(1,1,3,3,3,3,3,1,3)

temp <- detect_jump(vector,
				jump_years = 1,
				check_years = 1,
				min_jump = 0.025)

temp
```

```{r Calculating jumps}

data_wf <- data %>% 
	select(cou, year, starts_with("wf")) 

data_group <- data_wf %>%
	select(-wf_TBPC) %>% #zmienna przyjmuje wartość zero
	group_by(cou) %>%
	arrange(cou, year)

data_dynamics <- data_group %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~.x/dplyr::lag(.x)
	)) %>% 
	filter(year != 2008) %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~ purrr::accumulate(.x, \(acc, nxt) acc*nxt)
	)) 
```

```{r, choosing jumps}
jumps_args <- list(
				is.dynamic = TRUE,
				jump_years = 2,
				check_years = 2,
				min_jump = 0.1)

data_jumps <- jump_data_proces(jumps_args)

```

### Jumps summary - which variables have large number of countries?

```{r jumps_summary}
jumps_sum_df <- jumps_summary()

jumps_sum_df
```

## Jumps visualization

```{r countries_treated}
filter_jumps <- treated_columns(wf_GCI.A.02)
dict_cou %>% 
	filter(cou %in% filter_jumps) %>% 
	select(cou, country)

```

```{r countries jumps line plot}
visual_jumps(wf_GCI.A.02)
```

```{r Panel visualization}
visual_panel(wf_GCI.A.02)
```

## Modelling

Choose appropiate variable to model

```{r prepare data to model}
data_model <- data_to_model(wf_GCI.A.02)


```

Perform matching

```{r Panel Match, include = FALSE}

results <- suppressWarnings(invisible(my_matching(outcome = "y_ham",
							  iterations = 1000)))

```

```{r covariate balance}
results 
```

```{r}
vars_to_test <- jumps_sum_df %>% 
	filter(value > 10) %>%
	select(name) %>%  
	unlist()
# vars_to_test
names(vars_to_test) <- vars_to_test
vars_to_test_col <- vars_to_test
```

```{r Test many vars, include=FALSE}

test_variables <- function(var){
	data_model <- data_to_model({{var}}) # to trzeba poprawić
	results <- my_matching(iterations = 100,
								  df = data_model)
	results_df <- tibble(results = results) %>%
		mutate(results = map(results, .f = ~as.data.frame(.x))) %>% 
		mutate(names = names(results)) %>%
		unnest(cols = c(results)) %>% 
		select(names, everything())
	results_df
}
plan(multisession, workers = 4)
results_list <- furrr::future_map(vars_to_test,test_variables,
											 .options = furrr_options(seed = 123))
print("finish")
```

```{r Test summary}

all_df <- tibble(results = results_list) %>%
	mutate(variable = names(results)) %>%
	unnest(cols = c(results)) 
all_df_summary <- all_df %>%
	mutate(check = ifelse(`5%`> -0.005, 1, 0)) %>% 
	group_by(variable) %>% 
	summarize(sig_positive = mean(check)) %>% 
	left_join(dict_GCI, by = c("variable" = "variables")) %>% 
	arrange(desc(sig_positive))

# list_to_save <- list(all_df, all_df_summary)
# writexl::write_xlsx(list_to_save, "jumps_33_004_d_yham.xlsx")
all_df_summary


```

```{r,include=FALSE}
jumps_args_list <- list(
	is.dynamic = c(TRUE, FALSE),
	jump_years = 1:3,
	check_years = 2:5,
	min_jump = 
		seq(from = 0.01,
			by = 0.01,
				length.out = 10)) %>% 
	cross()

column <- "wf_GCI.A.04"

data_onevar <- one_var_df_proc(column = !!column)

vars_to_test <- data_onevar %>% 
	select(-year) %>% 
	group_by(cou) %>% 
	summarize(across(.cols = everything(),
						  .fns = max)) %>% 
	ungroup() %>% 
	select(-cou) %>% 
	select(where(~sum(.x)>10) & where(~sum(.x)<50) ) %>% ## only jumps where minimum 10 countries were detected
	colnames()


names(vars_to_test) <- vars_to_test


plan(multisession, workers = 4)
results_list <- furrr::future_map(vars_to_test, test_one_variable,
											 .options = furrr_options(seed = 123))
print("finish")

```

```{r}
all_df <- tibble(results = results_list) %>%
	mutate(variable = names(results)) %>%
	unnest(cols = c(results)) 
all_df_summary <- all_df %>%
	mutate(check = ifelse(`5%`> -0.005, 1, 0)) %>% 
	group_by(variable) %>% 
	summarize(sig_positive = mean(check)) %>% 
	arrange(desc(sig_positive))

list_to_save <- list(all_df, all_df_summary)
writexl::write_xlsx(list_to_save, paste0("results/jumps_",column,"_yham.xlsx"))

all_df_summary 

```

```{r}
data_model %>% 

	left_join(data_onevar %>% 
				 		mutate(cou = as.integer(as.factor(cou)))) %>%
	filter(year != 2008) %>% 
	select(cou, year, `1_3_2_0.1`, treatment) %>% 
	ungroup() %>% 
	summarize(x = sum(abs(`1_3_2_0.1`- treatment)))

```

```{r, include = FALSE}
test_everything <- function(variable){
	# variable <- enquo(variable)
	jumps_args_list <- list(
	is.dynamic = c(TRUE, FALSE),
	jump_years = 1:3,
	check_years = 2:5,
	min_jump = 
		seq(from = 0.01,
			by = 0.01,
				length.out = 10)) %>% 
	cross()

	data_onevar <- one_var_df_proc(column = !!variable)
	
	vars_to_test <- data_onevar %>% 
		select(-year) %>% 
		group_by(cou) %>% 
		summarize(across(.cols = everything(),
							  .fns = max)) %>% 
		ungroup() %>% 
		select(-cou) %>% 
		select(where(~sum(.x)>10) & where(~sum(.x)<50) ) %>% 
		colnames()
	if (length(vars_to_test) == 0){
		return(NULL)
	}
	names(vars_to_test) <- vars_to_test
	# return(list(vars_to_test, data_onevar))
	results_list <- map(vars_to_test, 
			  .f = ~test_one_variable(.x, data_one = data_onevar))
	all_df <- tibble(results = results_list) %>%
			mutate(variable = names(results)) %>%
			unnest(cols = c(results))
	all_df_summary <- all_df %>%
		mutate(check = ifelse(`5%`> -0.00, 1, 0)) %>%
		group_by(variable) %>%
		summarize(sig_positive = mean(check)) %>%
		arrange(desc(sig_positive))

	list_to_save <- list(all_df, all_df_summary)
	writexl::write_xlsx(list_to_save, paste0("results/jumps_",variable,"_yham.xlsx"))
	return(list(df = all_df_summary, name = variable))
}
 

plan(multisession, workers = 8)
final_results <- future_map(vars_to_test_col, safely(test_everything), .progress = TRUE,
			  .options = furrr_options(seed = 123))
print("finish")


```

```{r,echo=FALSE}
final_results_df <- final_results

final_results_tibble <- final_results_df %>% 
	map(.f = ~.x$result$df) %>% 
	map2(.y = names(final_results_df), ~.x %>% 
		  	cbind(name = .y)) %>% 
	discard(.p = ~!is.data.frame(.x)) %>%
	map(.f =~pivot_wider(.x, values_from = sig_positive)) %>% 
	reduce(.f = full_join, by = join_by(variable))

# write_xlsx(final_results_tibble, "results_all.xlsx")
```

```{r}
final_results_tibble %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	group_by(name) %>% 
	summarize(value = max(value)) %>% 
	arrange(desc(value)) %>% 
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series)
```
