# GDP growth caused by GCI indicators jumps with PanelMatch package

### Libraries

```{r Funkcje, echo=FALSE}
source("matching_functions.R")
options(scipen = 999)
```

```{r Biblioteki, echo = FALSE, include = FALSE}
library(tidyverse)
library(writexl)
library(panelView)
library(PanelMatch)
library(furrr)
library(readxl)
library(kableExtra)

# data <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\Nowy_projekt_BNK\2_Przetwarzanie_danych\Data_merging\database_2023_12_22.xlsx)")
# 
# data <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\2_Przetwarzanie_danych\Data_merging\database_2023_12_29.xlsx)")

data <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\2_Przetwarzanie_danych\Data_merging\database_2024_01_06.xlsx)")

# temp <- data %>% 
# 	glimpse()

dict_GCI <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\dict_master.xlsx)",
										sheet = "GCI") %>% 
	mutate(variables = paste0("wf_", variables))

dict_cou <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\dict_master.xlsx)")

dict_hier <- readxl::read_xlsx(r"(C:\Users\rados\OneDrive - SGH\project_matching_GCI\dict_hierarchical.xlsx)",
										 sheet = "Sheet1")

```

## Function to detect a jump

Assume, that jump exist if:

-   In period equal "jump_years" we have jump larger or equal "min_jump",

-   In period "check_years" - number of years after potential jump, level of variable doesn't drop, so jump is sustained

```{r Function to detect jumps}

detect_jump <- function(
		vector,
		jump_years = 3,
		check_years = 3,
		min_jump = 0.5){
	#version with results 2024-01-13
	len_vector = length(vector)
	vector_output <- rep(0,len_vector)
	for (ii in 1:len_vector){
		success <- FALSE
		# Count years which are necessary for letter actions
		if(len_vector -(ii+jump_years-1) <  check_years){
			# print(ii)
			break
		}
		# Jump period detecting:
		# Remember, for example for
		#jump period equal 2, we take vector with length 3!
		jump_period <- vector[ii:(ii+jump_years)]
		
		last_check_year <- len_vector
		# Check if in year in control period value level was lower that in the moment of jump:
		if((ii+jump_years+check_years) < len_vector){
			last_check_year <- (ii+jump_years+check_years)
		}
		#If jump_period is larger than one year, check narrower definition.
		#If they are satisfied, go next. (maybe it would better to make recursive call here?)
		earlier <- 0
		# print(c("before loop", ii))
		for(jj in (length(jump_period)-2):0){
			jump <- jump_period[jump_years -jj + 1] - jump_period[1]
			# print(c("jj", jj, jump))
			# Check minimum jump
			if(jump < min_jump){
				next
			}
			# print(c("jj", jj))
			# Check if length of vector to check is sufficient
			if((ii+jump_years+check_years-jj-1) < len_vector){
				last_check_year <- (ii+jump_years+check_years-jj-1)
				#Attention 1 at the end modify function so we evaluate with level before reform
			}
			# print(c("jj", jj))
			# print(list((ii+jump_years-jj):last_check_year, jump_period))
			# Check next years in case if variable drop below minimal level
			if(any(vector[(ii+jump_years-jj):last_check_year] - jump_period[jump_years-jj] < 0)){
				# print(ii)
				next
			}
			earlier <- jj
			success <- TRUE
			# print(c("jj", jj))
			break
		}
		# Indicate values of binary vector
		if(success){
			vector_output[(ii+jump_years - earlier):len_vector] <- 1
			break
		}
	}
	# print(c(ii))
	return(vector_output)
}

df <- tibble(
	v1 =  c(1,1,2,1,0,0,0,1,2,2),
	v2 =  c(1,1,2,2,1,0,0,1,2,2),
	v3 =  c(1,1.03,1.04,1.05,1.06,1.04,1.03,1.02,0,0)
)

df %>% 
	mutate(across(
		.cols = everything(),
		.fns = detect_jump, 
		jump_years  = 3,
		min_jump = 0.05,
		check_years = 3
	))




```

```{r Calculating jumps}

data_wf <- data %>% 
	# mutate(year = as.numeric(year)) %>% 
	select(cou, year, starts_with("wf"))

to_scale <- data_wf %>% 
	select(where(~min(.x) < 1) | where(~max(.x) > 7)) %>% 
	colnames()
to_scale <- setdiff(to_scale, c("cou","year"))

data_group <- data_wf %>%#zmienna przyjmuje wartość zero
	mutate(across(.cols = all_of(to_scale),
					  .fns = ~(.x - min(.x))/(max(.x) - min(.x)))) %>% 
	mutate(across(.cols = all_of(to_scale),
					  .fns = ~(.x + 1)*3.5)) %>% 
	group_by(cou) %>%
	arrange(cou, year) 


data_dynamics <- data_group %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~.x/dplyr::lag(.x)
	)) %>% 
	filter(year != 2008) %>% 
	mutate(across(
		.cols = starts_with("wf"),
		.fns = ~ purrr::accumulate(.x, \(acc, nxt) acc*nxt)
	)) 
# to_remove_dym <- data_dynamics %>% 
# 	filter(if_any(.fns = list(is.infinite, is.na))) %>% 
# 	ungroup() %>% 
# 	select(where(~any(is.infinite(.x)))) %>%
# 	colnames()
# 
# 
# data_dynamics <- data_dynamics %>% 
# 	select(-all_of(to_remove_dym))

```

```{r, choosing jumps}
jumps_args <- list(
				is.dynamic = TRUE,
				jump_years = 2,
				check_years = 3,
				min_jump = 0.05)

data_jumps <- jump_data_proces(jumps_args)


```

### Jumps summary - which variables have large number of countries?

```{r jumps_summary}
jumps_sum_df <- jumps_summary()

jumps_sum_df
```

## Jumps visualization

```{r countries_treated}
filter_jumps <- treated_columns(wf_GCI)
dict_cou %>% 
	filter(cou %in% filter_jumps) %>% 
	select(cou, country)

```

```{r countries jumps line plot}
visual_jumps(wf_GCI)
```

```{r Panel visualization}
visual_panel(wf_GCI)
```

## Modelling

Choose appropiate variable to model

```{r prepare data to model}
data_model <- data_to_model(wf_GCI)

# write_xlsx(data_model, "temp.xlsx")
```

Perform matching

```{r Panel Match, include = FALSE}

results <- suppressWarnings(invisible(
	my_matching(outcome = "y_ham",
				   iterations = 1000,
					matching_methods = c("CBPS.match","CBPS.weight"),
					periods = 2)
	))

```

```{r covariate balance}
my_matching(outcome = "y_ham",
				   iterations = 1000,
					matching_methods = c("CBPS.match","CBPS.weight"),
				get_balance = TRUE)
results
```

### Test all variables within one jump definition

```{r vars_to_col}
vars_to_test <- dict_GCI %>% 
	# filter(value > 10) %>%
	select(variables) %>%  
	unlist()
# vars_to_test
names(vars_to_test) <- vars_to_test
vars_to_test_col <- vars_to_test
```

```{r test many vars, include=FALSE}

test_variables <- function(var){
	data_model <- data_to_model({{var}}) # to trzeba poprawić
	results <- my_matching(iterations = 100,
								  df = data_model)
	results_df <- tibble(results = results) %>%
		mutate(results = map(results, .f = ~as.data.frame(.x))) %>% 
		mutate(names = names(results)) %>%
		unnest(cols = c(results)) %>% 
		select(names, everything())
	results_df
}
plan(multisession, workers = 4)
results_list <- furrr::future_map(vars_to_test,test_variables,
											 .options = furrr_options(seed = 123))
print("finish")
```

```{r Test summary}

all_df <- tibble(results = results_list) %>%
	mutate(variable = names(results)) %>%
	unnest(cols = c(results)) 
all_df_summary <- all_df %>%
	mutate(check = ifelse(`5%`> -0.005, 1, 0)) %>% 
	group_by(variable) %>% 
	summarize(sig_positive = mean(check)) %>% 
	left_join(dict_GCI, by = c("variable" = "variables")) %>% 
	arrange(desc(sig_positive))

# list_to_save <- list(all_df, all_df_summary)
# writexl::write_xlsx(list_to_save, "jumps_33_004_d_yham.xlsx")
all_df_summary


```

### Test one variable among many jumps definitions.

```{r,include=FALSE}
jumps_args_list <- list(
	is.dynamic = c(TRUE, FALSE),
	jump_years = 1:3,
	check_years = 2:5,
	min_jump = 
		seq(from = 0.01,
			by = 0.01,
				length.out = 10)) %>% 
	cross()

column <- "wf_GCI.A.04"

data_onevar <- one_var_df_proc(column = !!column)

vars_to_test <- data_onevar %>% 
	select(-year) %>% 
	group_by(cou) %>% 
	summarize(across(.cols = everything(),
						  .fns = max)) %>% 
	ungroup() %>% 
	select(-cou) %>% 
	select(where(~sum(.x)>15) & where(~sum(.x)<45) ) %>% ## only jumps where minimum 10 countries were detected
	colnames()


names(vars_to_test) <- vars_to_test


plan(multisession, workers = 4)
results_list <- furrr::future_map(vars_to_test, test_one_variable,
											 .options = furrr_options(seed = 123))
print("finish")

```

```{r}
all_df <- tibble(results = results_list) %>%
	mutate(variable = names(results)) %>%
	unnest(cols = c(results)) 
all_df_summary <- all_df %>%
	mutate(check_1  = ifelse(`5%`> 0.00, 1, 0)) %>%
	mutate(check_2  = ifelse(`95%`< 0.00, 1, 0)) %>%
	group_by(variable) %>%
	summarize(sig_positive = mean(check_1),
				 sig_negative = mean(check_2)) %>%
	arrange(desc(sig_negative))


list_to_save <- list(all_df, all_df_summary)
# writexl::write_xlsx(list_to_save, paste0("results/jumps_",column,"_yham.xlsx"))

all_df_summary 

```

```{r}
# data_model %>% 
# 	left_join(data_onevar %>% 
# 				 		mutate(cou = as.integer(as.factor(cou)))) %>%
# 	filter(year != 2008) %>% 
# 	select(cou, year, `1_3_2_0.1`, treatment) %>% 
# 	ungroup() %>% 
# 	summarize(x = sum(abs(`1_3_2_0.1`- treatment)))

```

### Test all combinations: many variables & many jump definition

```{r, include = FALSE}
test_everything <- function(variable){
	# variable <- enquo(variable)
	# jumps_args_list_1 <- list(
	# is.dynamic = c(FALSE),
	# jump_years = 1:3,
	# check_years = 2:3,
	# min_jump =
	# 	seq(from = 0.1,
	# 		by = 0.05,
	# 			length.out = 20)) %>% cross()
	jumps_args_list_2  <- list(
		is.dynamic = c(TRUE),
		jump_years = 1:3,
		check_years = 2:3,
		min_jump =
			seq(from = 0.05,
				by = 0.005,
					length.out = 24)) %>% cross()
	# jumps_args_list <- append(jumps_args_list_2, jumps_args_list_1)
	jumps_args_list <-  jumps_args_list_2
	data_onevar <- one_var_df_proc(column = !!variable,
											 list_jumps_args = jumps_args_list) %>% 
		filter(year != 2008)
	vars_to_test <- data_onevar %>% 
		select(-year) %>% 
		group_by(cou) %>% 
		summarize(across(.cols = everything(),
							  .fns = max)) %>% 
		ungroup() %>% 
		select(-cou) %>%  
		select(where(~sum(.x) > 20) & where(~sum(.x) < 60) ) %>% 
		colnames()
	if (length(vars_to_test) == 0){
		return(NULL)
	}	
	counts <- data_onevar %>%
		select(cou, all_of(vars_to_test)) %>% 
		group_by(cou) %>% 
		summarize(across(.cols = everything(),
							  .fns = max)) %>% 
		ungroup() %>% 
		select(-cou) %>% 
		summarize(across(.cols = everything(),
							  .fns = sum)) %>% 
		pivot_longer(cols = everything()) %>% 
		rename(count = value) %>% 
		rename(variable = name)
	# return(counts)
	

	names(vars_to_test) <- vars_to_test
	# return(list(vars_to_test, data_onevar))
	results_list <- map(vars_to_test, 
			  .f = ~test_one_variable(.x, 
  						data_one = data_onevar))
	all_df <- tibble(results = results_list) %>%
			mutate(variable = names(results)) %>%
			unnest(cols = c(results)) %>% 
			left_join(counts, by = "variable")
	all_df_summary <- all_df %>%
		mutate(check_1  = ifelse(`5%`> 0.00, 1, 0)) %>%
		mutate(check_2  = ifelse(`95%`< 0.00, 1, 0)) %>%
		group_by(variable, count) %>%
		summarize(sig_positive = mean(check_1),
					 sig_negative = mean(check_2)) %>%
		arrange(desc(sig_positive)) 
		
	list_to_save <- list(all_df, all_df_summary)
	writexl::write_xlsx(list_to_save, paste0("results_2024_01_10/jumps_20240110_",variable,"_yham.xlsx"))
	return(list(df = all_df_summary, name = variable))
}
 

plan(multisession, workers = 8)

filars_only <- vars_to_test_col[vars_to_test_col %>% str_detect("EOS")]
final_results <- future_map(filars_only, safely(test_everything), .progress = TRUE,
			  .options = furrr_options(seed = 123))
print("finish")

final_results
```

```{r,echo=FALSE}
final_results_df <- final_results

final_results_sig_positive <- final_results_df %>% 
	map(.f = ~.x$result$df) %>% 
	map2(.y = names(final_results_df), ~.x %>% 
		  	cbind(name = .y)) %>% 
	discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-sig_negative) %>% 
		 	pivot_wider(values_from = sig_positive)) %>% 
	reduce(.f = full_join, by = join_by(variable))

final_results_sig_negative <- final_results_df %>% 
	map(.f = ~.x$result$df) %>% 
	map2(.y = names(final_results_df), ~.x %>% 
		  	cbind(name = .y)) %>% 
	discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-sig_positive) %>% 
		 	pivot_wider(values_from = sig_negative)) %>% 
	reduce(.f = full_join, by = join_by(variable))
# write_xlsx(final_results_tibble, "results_all.xlsx")
```

```{r}
final_results_sig_negative  %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	group_by(name) %>% 
	summarize(value = max(value)) %>% 
	arrange(desc(value)) %>% 
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series)
```

### Reading files with results from folder

```{r}

results_files <- list.files("results_2024_01_10") 

filter_temp <- results_files %>% str_remove("jumps_") %>% str_remove("_yham.xlsx")
rest_to_test <- vars_to_test_col[!vars_to_test_col %in% filter_temp]

final_results_read <- paste0("results_2024_01_10\\", results_files) %>% 
	map(.f = function(x){
		sheet1 <- read_xlsx(x, sheet = "Sheet1")
		sheet2 <- read_xlsx(x, sheet = "Sheet2")
		to_return <- list(
			Sheet1 = sheet1,
			Sheet2 = sheet2,
			name = x %>% 
				str_remove("results_2024_01_10\\\\") %>% 
				str_remove("20240110_") %>%
				str_remove("jumps_") %>%
				str_remove("_yham.xlsx"))
	}) 
```

### How significance of results is distributed?

```{r}

final_results_sig_positive <- 
	final_results_read %>% 
	map(.f = ~.x$Sheet2) %>% 
	map2(.y = final_results_read, 
		  ~.x %>% cbind(name = .y$name)) %>% 
	# discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-c(count, sig_negative)) %>% 
		 	pivot_wider(values_from = sig_positive)) %>% 
	reduce(.f = full_join, by = join_by(variable)) %>% 
	arrange(variable)

final_results_sig_negative <- 
	final_results_read %>% 
	map(.f = ~.x$Sheet2) %>% 
	map2(.y = final_results_read, 
		  ~.x %>% cbind(name = .y$name)) %>% 
	# discard(.p = ~!is.data.frame(.x)) %>%
	map(.f = ~.x %>%
		 	select(-c(count, sig_positive)) %>% 
		 	pivot_wider(values_from = sig_negative)) %>% 
	reduce(.f = full_join, by = join_by(variable)) %>% 
	arrange(variable)
# writexl::write_xlsx(list(
# 	final_results_sig_negative,
# 	final_results_sig_positive),
# 	"all_results_2023_12_29.xlsx"
# )
```

```{r}
sig_pos_summary <- final_results_sig_positive  %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	group_by(name) %>% 
	summarize(value = max(value, na.rm = TRUE)) %>%
	# summarize(value = mean(value, na.rm = TRUE)) %>%
	arrange(desc(value)) %>% 
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series) %>% 
	rename(pos = value)

sig_neg_summary <- final_results_sig_negative  %>% 
	pivot_longer(-variable) %>% 
	drop_na() %>% 
	group_by(name) %>% 
	summarize(value = max(value, na.rm = TRUE)) %>%
	# summarize(value = mean(value, na.rm = TRUE)) %>%
	arrange(desc(value)) %>%
	left_join(dict_GCI, by = c("name" = "variables")) %>% 
	select(name, value, series) %>% 
	rename(neg = value)

all_summary <- sig_neg_summary %>% 
	left_join(sig_pos_summary,
				 by = join_by(name, series)) %>% 
	select(name, neg, pos, series) %>% 
	filter(str_detect(name, "\\.\\w{1}\\.\\d{2}|GCI|EOSQ")) %>% 
	arrange(desc(neg))

all_summary

```

```{r}
final_results_sig_positive %>% 
	summarize(across(
		-variable,
		.fns = ~mean(.x, na.rm = TRUE)
	)) %>% 
	pivot_longer(everything()) %>% 
	summarize(value = mean(value))

final_results_sig_negative %>% 
	summarize(across(
		-variable,
		.fns = ~mean(.x, na.rm = TRUE)
	)) %>% 
	pivot_longer(everything()) %>% 
	summarize(value = mean(value))
```

### Let's see...

```{r}
final_estimates <- final_results_read %>% 
	map(.f = ~.x$Sheet1 %>% 
		 	mutate(name = .x$name)) %>% 
	reduce(bind_rows) %>% 
	group_by(variable, name) %>% 
	mutate(sig_pos = ifelse(`5%` > 0,1,0), 
			 sig_neg = ifelse(`95%` < 0, 1,0)) %>% 
	summarize(across(
		.cols = all_of(c('5%', '95%','estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	group_by(name) %>% 
	summarize(across(
		.cols = all_of(c('5%', '95%','estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	ungroup()

final_est  <- 
	final_results_read %>%
	map(.f = ~.x$Sheet1 %>% 
		 	mutate(name = .x$name)) %>% 
	reduce(bind_rows) %>%
	filter(count >= 20) %>% 
	filter(str_detect(name, "\\.\\w{1}\\.\\d{2}|GCI")) %>%
	# filter(str_detect(name, "EOS")) %>%
	filter(names == "CBPS.weight") %>%
	separate(variable,
				into = c("is.dynamic",
						  "jump_years",
						  "check_years",
						  "min_jump"),
				sep = "_") %>% 
	# filter(is.dynamic == 0 & min_jump > 0.25) %>%
	filter(is.dynamic == 1 & min_jump >= 0.05) %>%
	filter(check_years == 3) %>% 
	unite(all_of(c("is.dynamic",
			  "jump_years",
			  "check_years",
			  "min_jump")),
			col = "variable") %>% 
	mutate(sig_pos = ifelse(`5%` > 0,1,0), 
			 sig_neg = ifelse(`95%` < 0, 1,0)) %>% 
	group_by(name) %>% 
	mutate(count_defs = accumulate(variable,
						.f = append)) %>% 
	mutate(count_defs = map(count_defs,
						.f = ~unique(.x) %>% length())) %>% 
	mutate(count_defs = max(unlist(count_defs))) %>% 
	group_by(variable, name, names) %>% 
	mutate(year = row_number()) 
	 
	
final_est_by_year <- final_est %>% 
	group_by(variable, name, year, count_defs) %>%  
	summarize(across(
		.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	group_by(name, year, count_defs) %>% 
	summarize(across(
		.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
		.fns = mean
	)) %>% 
	ungroup()  %>% 
	pivot_wider(values_from = all_of(c('estimate', 'sig_pos', 'sig_neg')), 
					names_from = 'year',
					names_glue = "{.value}_{year}") 

final_est_by_year_sum <- 
	final_est_by_year %>% 
	mutate(across(
		.cols = contains("estimate"),
		.fns = ~ifelse(.x > 0, 1, 0)))
summary(final_est_by_year_sum)
summary(final_est_by_year)

# final_est_by_year %>% 
# 	filter(if_any(.cols = everything(),
# 					  .fns = ~ is.na(.x)))


```

### Some tables to article

```{r summary tables}
table_by_year_sum <- final_est_by_year %>% 
	select(-name) %>% 
	summarize(across(
		.cols = -c(count_defs),
		.fns = mean))  %>% 
	# cbind(
	# final_est_by_year %>%
	# 	select(-name) %>%
	# 	summarize(across(
	# 		.cols = -c(count_defs),
	# 		.fns = ~weighted.mean(.x,count_defs))) %>%
	# 	rename_with(.fn = ~paste0("w.",.x))) %>%
	cbind(
		final_est_by_year %>% 
			mutate(across(
				.cols = contains("estimate"),
				.fns = ~ifelse(.x > 0, 1, 0))) %>% 
			select(-name) %>% 
			summarize(across(
				.cols = everything(),
				.fns = mean)) %>% 
			select(estimate_1, estimate_2, estimate_3) %>% 
			rename_with(.fn = ~str_replace(.x,"estimate","proc"))) %>% 
	pivot_longer(
		cols = everything(),
		names_to = c(".value", "period"),
		names_pattern = "(.+?)_(\\d)") 

# writexl::write_xlsx(table_by_year_sum, "table_by_year_sum_2024_01_13.xlsx")

```

## Nie zbyt mądra próba modelowania, czy parametr ma wpływ na zmienną?

```{r}

# final_results_sig_negative %>% 
# 	pivot_longer(-variable) %>% 
# 	drop_na() %>% 
# 	rename(sig_neg = value) %>% 
# 	left_join(final_results_sig_positive %>% 
# 	 	pivot_longer(-variable) %>% 
# 		drop_na() %>% 
# 		rename(sig_pos = value)) %>% 
# 	mutate(value = sig_pos - sig_neg) 
pilar_1_to_rem <- dict_GCI %>% 
	filter(str_detect(variables, "GCI")) %>% 
	filter(!is.na(b) & is.na(c)) %>% 
	select(series) %>% 
	unlist() 

table_results <- final_est_by_year %>% 
	full_join(dict_GCI %>% 
				 	filter(str_detect(variables, "GCI")),
				 by = c("name" = "variables")) %>% 
	select(name, series, everything()) %>%
	left_join(dict_hier %>% 
				 	select(matches("name_[234]|trans_[34]")),
				 by = c("series_unindented" = "name_4")) %>% 
	unite(c(name_2, name_3,series_unindented), 
			col = "series_unindented", 
			sep = ", ",
			na.rm = TRUE) %>% 
	unite(c(trans_3, trans_4), 
			col = "trans", 
			sep = ", ",
			na.rm = TRUE) %>% 
	left_join(dict_hier %>%
				 	select(matches("name_[23]|trans_[3]"))%>% 
				 	distinct(),
				 by = c("series_unindented" = "name_3")) %>% 
	unite(c(trans_3, trans), 
			col = "trans", 
			sep = "",
			na.rm = TRUE) %>% 
	unite(c(name_2, series_unindented), 
			col = "series_unindented", 
			sep = ", ",
			na.rm = TRUE) 
	

table_results_2 <- table_results %>% 
	mutate(b = ifelse(is.na(b), 0, b)) %>% 
	arrange(a,b,series_unindented) %>% 
	extract(series_unindented, 
			  regex = "(\\d{1,2})\\w{2,3} pillar: ", 
			  into = "pilar",
			  remove = FALSE) %>% 
	mutate(series_unindented = ifelse(series_unindented %in% pilar_1_to_rem,
												 series_unindented,
												 str_remove(series_unindented, "^\\d{1,2}.+?,\\s"))) %>% 
	select(a,pilar,trans, series_unindented, count_defs, matches("estimate"), matches("^sig_pos"))
# exp(0.0098)

table_results_3 <- table_results %>%
	group_by(name) %>% 
	mutate(max_sig = max(c_across(contains("sig_pos")))) %>% 
	mutate(min_sig = max(c_across(contains("sig_neg")))) %>% 
	arrange(desc(max_sig)) %>% 
	head(15) %>% 
	mutate(b = ifelse(is.na(b), 0, b)) %>% 
	arrange(a,b,series_unindented) %>% 
	extract(series_unindented, 
			  regex = "(\\d{1,2})\\w{2,3} pillar: ", 
			  into = "pilar",
			  remove = FALSE) %>% 
	mutate(series_unindented = ifelse(series_unindented %in% pilar_1_to_rem,
												 series_unindented,
												 str_remove(series_unindented, "^\\d{1,2}.+?,\\s"))) %>% 
	select(a,pilar, series_unindented, count_defs, matches("estimate"), matches("^sig_pos"))
	# mutate(across(.cols = contains("sig_pos"),
	# 				  .fns = ~rank(-.x, ties.method = "last"),
	# 				  .names = "rank_{.col}")) %>%
	# select(name, series, contains("sig_pos"), everything()) %>%
	# arrange(desc(sig_pos_3)) #%>%
# 	filter(rank_sig_pos_3 < 6 |
# 			 	name %in% c("wf_GCI.B.05.01", "wf_GCI.B.05")) %>% 
#  	select(name, count_defs, letters[1:4], series, matches("estimate"), matches("^sig_pos")) %>% 
# 	left_join(dict_GCI %>% 
# 				 	filter(is.na(c)) %>% 
# 				 	select(a,b, series), by = c("a","b")) %>% 
# 	mutate(series.x = ifelse(series.x == series.y, series.x
# 									 , paste0(series.y, " ", series.x))) %>% 
# 	select(series.x, count_defs, matches("estimate"), matches("^sig_pos")) 
		
# write_xlsx(table_results, "table_results2.xlsx")
# write_xlsx(table_results_3, "table_results_full_2024_01_11_head.xlsx")
```
### Plots:
```{r plots - histogram}
final_est_by_year %>% 
	ggplot(aes(x = estimate_3)) + 
	geom_histogram(
		bins = 20,
		aes(y = after_stat(count),
			 alpha = 0.5),
		show.legend = FALSE) +
	stat_density(geom = "line",
					 aes(y = ..count.. *0.01)) +
	geom_rug() +
	xlim(c(-0.08,0.08)) +
	theme_bw() +
	theme(legend.key = element_blank(),
			legend.text = element_blank(),
			axis.title.x = element_blank(),
			axis.title.y = element_blank())
```
```{r ribbons}
df_errorbars <- final_est %>% 
	group_by(variable, name, year, count_defs) %>%  
	summarize(across(
		.cols = all_of(c('5%', '95%', 'estimate')),
		.fns = mean
	)) %>% 
	group_by(name, year, count_defs) %>% 
	summarize(across(
		.cols = all_of(c('5%', '95%', 'estimate')),
		.fns = mean
	)) %>% 
	mutate(name = as.factor(name)) %>% 
	left_join(dict_GCI %>% 
				 	filter(str_detect(variables, "GCI")),
				 by = c("name" = "variables")) %>% 
	filter(is.na(b)) %>% 
	rename(lower = `5%`, 
			 upper = `95%`) %>% 
	mutate(year = as.factor(year -1)) %>% 
	ungroup() %>% 
	left_join(dict_hier %>% 
				 	distinct(name_1, trans_1),
				 by = c("series" = "name_1")) %>%
	mutate(group = as.factor(paste0(a,". ",trans_1))) %>% 
	ungroup() %>% 
	mutate(grid = ifelse(row_number()>6, "B-C","GCI-A")) %>% 
	mutate(grid = factor(grid))
	

# glimpse(df_errorbars)

p <- ggplot(df_errorbars, 
				aes(x = year, 
					 y = estimate,
					 color = group)) +
	geom_point(aes(shape = group),
				  alpha = 0.9,
				  size = 5) +
	geom_line(aes(group = group)) +
	geom_errorbar(aes(ymin = lower, ymax = upper), 
					  width = 0.2,
					  alpha = 0.9) +
	theme_minimal() +
	scale_shape_manual(values = c(15:19)) +
	labs(x = "Lata po reformie") +
	geom_hline(yintercept = 0, linetype = "solid", color = "black", size = 0.5) +
	theme(axis.title.y = element_blank(),
			text = element_text(family = "serif", size = 16),
			legend.title = element_text(size = 16, face = "bold"),
			axis.text.x = element_text(color = "black")) +
	facet_wrap(vars(grid)) +
	ylim(c(-0.1,0.1)) +
	 guides(
    color = guide_legend(title = "Główne agregaty", override.aes = list(linewidth  = NA)),
    shape = guide_legend(title = "Główne agregaty"),
    alpha = FALSE)
p


ggsave(filename = "main_aggs.png", plot = p, device = "png",
		 width = 10,
		 height = 4,
		 scale = 1)


```



```{r ribbons2}
df_errorbars2 <- final_est %>% 
	group_by(variable, name, year, count_defs) %>%  
	summarize(across(
		.cols = all_of(c('5%', '95%', 'estimate')),
		.fns = mean
	)) %>% 
	group_by(name, year, count_defs) %>% 
	summarize(across(
		.cols = all_of(c('5%', '95%', 'estimate')),
		.fns = mean
	)) %>% 
	mutate(name = as.factor(name)) %>% 
	left_join(dict_GCI %>% 
				 	filter(str_detect(variables, "GCI")),
				 by = c("name" = "variables")) %>% 
	left_join(dict_hier %>% 
				 	distinct(name_2, trans_2),
				 by = c("series" = "name_2")) %>%  
	filter(is.na(c)&!is.na(b)) %>% 
	rename(lower = `5%`, 
			 upper = `95%`) %>% 
	mutate(year = as.factor(year -1)) %>% 
	mutate(group = as.factor(trans_2)) %>% 
	ungroup() %>% 
	group_by(name) %>% 

	extract(series_unindented, 
			  regex = "(\\d{1,2})\\w{2,3} pillar: ", 
			  into = "pilar",
			  remove = FALSE) %>% 
	mutate(grid = floor((as.numeric(pilar)-1)/2)) %>% 
	mutate(grid = paste0(((grid)*2+1),"-",(grid)*2+2)) %>% 
	mutate(grid = as.factor(grid))
# glimpse(df_errorbars)

p2 <- ggplot(df_errorbars2, 
				aes(x = year, 
					 y = estimate,
					 color = group)) +
	geom_point(aes(shape = group),
				  size = 3) +
	geom_line(aes(group = group)) +
	geom_errorbar(aes(ymin = lower, ymax = upper), 
					  width = 0.2,
					  alpha = 0.8) +
	theme_minimal() +
	labs(x = "Lata po reformie") +
	geom_hline(yintercept = 0, linetype = "solid", color = "black", size = 0.5) +
	scale_shape_manual(values = c(15:26)) +
	scale_color_manual(values = rep(c("red","blue"),6)) +
	theme(axis.title.y = element_blank(),
			text = element_text(family = "serif", size = 16),
			legend.title = element_text(size = 16, face = "bold"),
			axis.text.x = element_text(color = "black")) +
	ylim(c(-0.1,0.1)) +
	# plot.margin = margin(1, 1, 1, 1, "cm") +
	guides(
    color = guide_legend(title = "Filary GCI", override.aes = list(linewidth  = NA)),
    shape = guide_legend(title = "Filary GCI"),
    alpha = FALSE) +
	facet_wrap(vars(grid))

ggsave(filename = "pilars_aggs.png", plot = p2, device = "png",
		 width = 10,
		 height = 5)
p2
```
```{r}
df_test_model <- 
	final_results_read %>% 
	map(.f = ~.x$Sheet2) %>% 
	map2(.y = final_results_read, 
		  ~.x %>% cbind(name = .y$name)) %>% 
	reduce(.f = full_join,
			 by = join_by(variable, count, sig_positive, sig_negative, name)) %>% 
	left_join(final_results_read %>% 
		map(.f = ~.x$Sheet1 %>% 
			 	mutate(name = .x$name)) %>% 
		reduce(bind_rows) %>% 
		group_by(variable, name) %>% 
		mutate(sig_pos = ifelse(`5%` > 0,1,0), 
				 sig_neg = ifelse(`95%` < 0, 1,0)) %>% 
		summarize(across(
			.cols = all_of(c('estimate', 'sig_pos', 'sig_neg')),
			.fns = mean
		))) %>% 
	arrange(variable) %>% 
	separate(variable,
				into = c("is.dynamic",
						  "jump_years",
						  "check_years",
						  "min_jump"),
				sep = "_") %>% 
	mutate(sig_sum = sig_positive - sig_negative) %>% 
	mutate(across(-name,
					  .fns = ~as.numeric(.x))) %>% 
	mutate(sig_bin = ifelse(sig_sum > 0, 1, 0))
```

```{r}
model_lm <- lm(estimate ~ 
						factor(jump_years) +
						# factor(is.dynamic):factor(jump_years) + 
						# factor(min_jump) +
						# factor(is.dynamic):factor(check_years) +
						# factor(is.dynamic):count +
						# factor(check_years) +
						count +
						min_jump +
						name,
						data = df_test_model %>% 
						filter(is.dynamic == 1) %>% 
						filter(str_detect(name, "\\.\\w{1}\\.\\d{2}|GCI|EOS"))
						)
summary(model_lm)

# model_glm <- glm(sig_bin ~ is.dynamic +
# 						factor(is.dynamic):jump_years + 
# 						factor(is.dynamic):min_jump +
# 						factor(is.dynamic):check_years +
# 						factor(is.dynamic):count +
# 						name,
# 						data = df_test_model,
# 						family = binomial(link = "logit")
# 						)
# summary(model_glm)

# citation("PanelMatch")
# glue::glue_collapse(vars_to_test_col, sep = "\n")
```
